---
title: "Corpus Preparation"
subtitle: "Submitted to Interspeech 2021"
output: html_notebook
author: Xiao Xiao 
---

This documents contains scripts that load assets for references for comparisons with subject recordings.
There's also some comparison within the reference corpus to see the quantitative difference between original and stylized pitch curves (very similar) and between pairs of phrases.

# Load assets for reference phrases

This code section should be run before running code in 02-compare-vocal.Rmd and 03-compare-gestural.Rmd

```{r}
library("tidyverse")
library("rPraat") # to load Praat objects
library("zoo") # for interpolation of gesture data
source("utils/hz2st.r")

# Reference frequency for conversion from hertz to semitones
ref_freq <- 116.54

# A vector with all the phrases
ref_phrases<- c("2_tu_parais_tres_soucieux", "2bis_tu_paraitrais_soucieux",
                "7_Jean_leve_son_verre", "7bis_Jenleve_son_verre", 
                "8_jean_porte_un_journal","8bis_jemporte_un_journal",
                "10_jean_saigne_beaucoup", "10bis_jenseigne_beaucoup",
                "11_jean_cadre_la_photo", "11bis_jencadre_la_photo",
                "21_cest_la_mort_sure", "21bis_cest_la_morsure")      
 
# All the reference pitchtiers, not interpolated
ref_pts <- lapply(ref_phrases, function(name) {
    my_pt<-pt.read(paste0("data/reference/pt/",name,".PitchTier"))
})

# Reference pitchtiers, interpolated by 0.01-second intervals
ref_pts_interp <- lapply(ref_phrases, function(name) {
    my_pt<-pt.read(paste0("data/reference/pt/",name,".PitchTier"))
    interpolated <- pt.interpolate(my_pt, seq(0, my_pt$tmax, by=0.01))
    interpolated$f <- hertz_to_semitones(interpolated$f, ref_freq)
    interpolated
})
 
# All the reference Prosograms (stylized pitchtiers), not interpolated
ref_psgs <- lapply(ref_phrases, function(name) {
  my_pt<-pt.read(paste0("data/reference/prosogram_pt/", name, "_styl.PitchTier"))
})

# Reference Prosograms, interpolated by 0.01-second intervals
ref_psgs_interp <- lapply(ref_phrases, function(name) {
  my_pt<-pt.read(paste0("data/reference/prosogram_pt/", name, "_styl.PitchTier"))
  interpolated <- pt.interpolate(my_pt, seq(0, my_pt$tmax, by=0.01))
  interpolated$f <- hertz_to_semitones(interpolated$f,ref_freq)
  interpolated
})

# Non-interpolated reference intensity tiers
ref_its <- lapply(ref_phrases, function(name) {
  my_it <- it.read(paste0("data/reference/intensity/", name, ".IntensityTier"))
})

# Reference intensity tiers, interpolated by 0.01-second intervals
ref_its_interp <- lapply(ref_phrases, function(name) {
  my_it <- it.read(paste0("data/reference/intensity/", name, ".IntensityTier"))
  it.interpolate(my_it, seq(0, my_it$tmax, by=0.01))
})

# Put all the reference textgrids into a list
ref_tgs <- lapply(ref_phrases, function(name) {
  tg.read(paste0("data/reference/tg/", name, '_auto.TextGrid'))
})

# Get the times of each phrase
ref_times <- do.call("rbind", lapply(ref_pts_interp, function(item) {
  item$tmax
}))[,1]

# A tibble containing each phrase and its duration
ref_info <- tibble(phrase=ref_phrases, duration=ref_times)

###################################
# Helper functions for comparison #
###################################

# Get the TextGrid
get_ref_tg <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_tgs[[index]])
}

# Gets the interpolated prosogram object
get_ref_psgs_interp <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_psgs_interp[[index]])
}

# Gets interpolated pitchtier for reference
get_ref_pts_interp <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_pts_interp[[index]])
}

# A function that gets the duration given the phrase name
get_ref_duration <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_info$duration[index])
}

# Get the times stamps for interpolation given the phrase name
get_ref_timestamps <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_pts_interp[[index]]$t)
}

# Get the interpolated frequency values given the phrase name
# (frequency time series)
get_ref_tsf <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_pts_interp[[index]]$f)
}

# Get the interpolated prosogram frequency values given the phrase name
# (prosogram frequency time series)
get_ref_ptsf <- function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_psgs_interp[[index]]$f)
}

# Get the interpolated intensity values given the phrase name
# (intensity time series)
get_ref_tsi <-function(phrase_name) {
  index<-match(phrase_name, ref_info$phrase)
  if (is.na(index)) { return(NULL) }
  return(ref_its_interp[[index]]$i)
}
```


# Comparing Praat and Prosogram versions of the same phrase

Very high correlation and low RMSE (around 1 semitone) between pitch curve and its stylization.

```{r}
library("wCorr") # for the weighted correlation function
library("mltools") # for the weighted RMSE function

get_weighted_corr_praat_psg <- function(index) {
  praat_pitch <- ref_pts_interp[[index]]$f
  prosogram_pitch <- ref_psgs_interp[[index]]$f
  intensity <- ref_its_interp[[index]]$i
  
  wc <- weightedCorr(praat_pitch, prosogram_pitch, method = "Pearson", 
               weights = intensity, ML = FALSE, fast = TRUE)
  return(wc)
}

get_rmse_praat_psg <- function(index) {
  praat_pitch <- ref_pts_interp[[index]]$f
  prosogram_pitch <- ref_psgs_interp[[index]]$f
  intensity <- ref_its_interp[[index]]$i
  
  r <- rmse(preds=praat_pitch, actuals=prosogram_pitch, weights=intensity)
  return(r)
}

indices<-seq(1, 12)

wcorr_praat_psg_refs <- do.call("rbind", lapply(indices, function(item) {
  get_weighted_corr_praat_psg(item)
}))[,1]

rmse_praat_psg_refs <- do.call("rbind", lapply(indices, function(item) {
  get_rmse_praat_psg(item)
}))[,1]

scores_praat_prosogram <- tibble(phrase=ref_phrases, corr.praat.psg=wcorr_praat_psg_refs,
                                        rmse.praat.psg=rmse_praat_psg_refs)

mean(scores_praat_prosogram$corr.praat.psg) #0.9485677
sd(scores_praat_prosogram$corr.praat.psg) #0.03099698
mean(scores_praat_prosogram$rmse.praat.psg) #1.110687
sd(scores_praat_prosogram$rmse.praat.psg) #0.3209581

print(as.matrix(scores_praat_prosogram), quote = FALSE)

```

# Comparing Prosograms between pairs of phrases

Comparing both original and stylized pitch curves between pairs of phrases. In general, correlation is lower and RMSE is higher than comparison between the original and stylized pitch curve of the same phrase. Between some pairs (e.g. 2 and 2bis), correlation can still be quite high. RMSE is consistently higher by about 2 semitones.

```{r}
pbis <- c(2, 4, 6, 8, 10, 12)
#ref_pairs<-tibble(pid=pbis-1,phrase=ref_phrases[pbis-1], pid_bis=pbis, phrase_bis=ref_phrases[pbis])

psg_pairs_interp<-do.call("rbind", lapply(pbis, function(id) { 
  psg1<-ref_psgs[[id]]
  psg2<-ref_psgs[[id-1]]
  
  pt1<-ref_pts[[id]]
  pt2<-ref_pts[[id-1]]
  
  tmax <- max(psg1$tmax, psg2$tmax)
  len_to_interp <- seq(0, tmax, by=0.01) %>% length()
  
  psg1_interp<-pt.interpolate(psg1, seq(0, psg1$tmax, length=len_to_interp))
  psg2_interp<-pt.interpolate(psg2, seq(0, psg2$tmax, length=len_to_interp))
  
  pt1_interp<-pt.interpolate(pt1,  seq(0, pt1$tmax, length=len_to_interp))
  pt2_interp<-pt.interpolate(pt2,  seq(0, pt2$tmax, length=len_to_interp))
  
  it1<-ref_its[[id]]
  it1_interp<-it.interpolate(it1, seq(0, it1$tmax, length=len_to_interp))
  
  f1_psg<- hertz_to_semitones(psg1_interp$f, ref_freq)
  f2_psg<- hertz_to_semitones(psg2_interp$f, ref_freq)
  f1_pt<- hertz_to_semitones(pt1_interp$f, ref_freq)
  f2_pt<- hertz_to_semitones(pt2_interp$f, ref_freq)
  
  my_corr_psg<-weightedCorr(f1_psg, f2_psg, method = "Pearson", weights = it1_interp$i, ML = FALSE, fast = TRUE)
  my_rmse_psg<-rmse(preds=f1_psg, actuals=f2_psg, weights=it1_interp$i)
  
  my_corr_pt<-weightedCorr(f1_pt, f2_pt, method = "Pearson", weights = it1_interp$i, ML = FALSE, fast = TRUE)
  my_rmse_pt<-rmse(preds=f1_pt, actuals=f2_pt, weights=it1_interp$i)
  
  return(tibble(phrase=ref_phrases[[id-1]], phrase.bis=ref_phrases[[id]],
                corr.psg=my_corr_psg, rmse.psg=my_rmse_psg, corr.pt=my_corr_pt, rmse.pt=my_rmse_pt))
}))
  
mean(psg_pairs_interp$corr.psg) #0.5537139
sd(psg_pairs_interp$corr.psg) #0.4369208

mean(psg_pairs_interp$rmse.psg) # 4.040714
sd(psg_pairs_interp$rmse.psg) #0.5109039

print(as.matrix(psg_pairs_interp), quote = FALSE)
```


