---
title: "Plots"
output: html_notebook
---

# Prerequisites

Scores for voice and gesture data are saved in data/scores/voice_scores.rds data/scores/gest_scores.rds from running scripts in 02-compare-vocal.rmd and 03-compare-gesture.rmd.

The scores from prosogram comparisons are kept for gesture data, and the scores from the pitch tier comparisons are kept for the voice data. These are saved in data/scores/gest_scores_psg.rds and data/scores/voice_scores_pt.rds.

# Prepare the data

```{r}
# Load the score data
voice_data <- readRDS("data/scores/voice_scores.rds")
gests_data <- readRDS("data/scores/gest_scores.rds")

# Subjects and types
subjects <- read_tsv("data/subjects.tsv")
natives <- subjects %>% filter(lvl_french == "N")
learners <- subjects %>% filter(lvl_french != "N")
musicians <- subjects %>% filter(music == "Y")
nonmus <- subjects %>% filter(music != "Y")

# Add some info
gests_data <- gests_data %>% 
              mutate(native=ifelse(subject %in% natives$id, 0.5, -0.5)) %>%
              mutate(music=ifelse(subject %in% musicians$id, 0.5, -0.5)) %>%
              mutate(condition=type) %>% mutate(type="gesture")

# For gestures, we care most about comparison with the prosogram
gests_data_modified <- gests_data %>%
              mutate(corr=corr_psg, rmse=rmse_psg, 
                     corr_nt=corr_psg_notiming, rmse_nt=rmse_psg_notiming) %>%
              select(subject, native, music, condition, type, pid, order, phrase, id, 
                     corr, rmse, corr_nt, rmse_nt)
              
# Add some info.
voice_data <- voice_data %>% 
              mutate(native=ifelse(subject %in% natives$id, 0.5, -0.5)) %>%
              mutate(music=ifelse(subject %in% musicians$id, 0.5, -0.5)) %>%
              mutate(condition=type) %>% mutate(type="voice") 


# For voice, we care most about comparison with original curve                
voice_data_modified <- voice_data %>%
              mutate(corr_nt=corr_notiming, rmse_nt=rmse_notiming) %>%
              select(subject, native, music,condition, type, pid, order, phrase, id, 
                     corr, rmse, corr_nt, rmse_nt)
  
all_data <- bind_rows(gests_data_modified, voice_data_modified)

saveRDS(all_data, "all_scores.rds")
saveRDS(gests_data_modified, "gest_scores_psg.rds")
#saveRDS(voice_data_modified, "voice_scores_pt.rds")

# Vocal & Chironomic guided imitation
data_im <- all_data %>% 
           filter(condition == "imitation" | condition == "guide") %>% 
           mutate(vocal=ifelse(condition=="imitation", 0.5, -0.5)) %>%
           mutate(corr_nt_z = fisherz(corr_nt), corr_z = fisherz(corr), 
                  log_r = log(rmse), log_rnt= log(rmse_nt)) %>%
          mutate(pid = fct_relevel(pid, "2", "2bis", "7", "7bis", "8", "8bis",
                           "10", "10bis", "11", "11bis", "21", "21bis"))

# Chironomic imitation, guide/not contrast coded
data_chiro <- gests_data_modified %>% 
           mutate(guide=ifelse(condition=="guide", 0.5, -0.5)) %>%
           mutate(corr_nt_z = fisherz(corr_nt), corr_z = fisherz(corr), 
                    log_r = log(rmse), log_rnt= log(rmse_nt)) %>%
          mutate(pid = fct_relevel(pid, "2", "2bis", "7", "7bis", "8", "8bis",
                           "10", "10bis", "11", "11bis", "21", "21bis"))

```

# Plots; by phrase

```{r}
# Switch the order of voice & gesture so that guided timing/no-timing is lined up
data_im2 <- all_data %>% 
           filter(condition == "imitation" | condition == "guide") %>% 
           mutate(vocal=ifelse(condition=="imitation", -0.5, 0.5)) %>%
           mutate(corr_nt_z = fisherz(corr_nt), corr_z = fisherz(corr), 
                  log_r = log(rmse), log_rnt= log(rmse_nt)) %>%
          mutate(pid = fct_relevel(pid, "2", "2bis", "7", "7bis", "8", "8bis",
                           "10", "10bis", "11", "11bis", "21", "21bis"),
                 subject=fct_relevel(subject, "s1", "s2", "s3", "s4", "s5", "s6",
                           "s7", "s8", "s9", "s10"))
# BY PHRASE


corr_by_phrase <- 
       ggplot(data=data_im2, aes(x=pid, y=corr_nt)) + 
       geom_boxplot(aes(color=as_factor(vocal)), show.legend = FALSE, lwd=1.25, fatten=2) +
       geom_boxplot(data=data_chiro, aes(x=pid, y=corr, color=condition), 
                    alpha=0.4, show.legend = FALSE,lwd=1.25,fatten=2) +
       #scale_color_discrete(name="",labels=c("Voice,\nno timing", "Guided,\nno timing", 
      #                               "Non-guided,\nwith timing", "Guided,\nwith timing")) +
             scale_y_continuous(breaks=seq(-0.8, 1, by=0.2)) +
             labs(subtitle="Correlation scores by phrase", x="Phrase", y="Correlation") + 
  
             theme_bw(base_size=27) +
             theme(legend.text=element_text(size=18),
                   axis.title=element_text(size=20))

rmse_by_phrase <-
       ggplot(data=data_im2, aes(x=pid, y=rmse_nt)) + 
       geom_boxplot(aes(color=as_factor(vocal)), show.legend = FALSE, lwd=1.25,fatten=2) +
       geom_boxplot(data=data_chiro, aes(x=pid, y=rmse, color=condition), 
                    alpha=0.4, show.legend = FALSE,lwd=1.25,fatten=2) +
       #scale_color_discrete(name="",labels=c("Voice,\nno timing", "Guided,\nno timing", 
      #                             "Non-guided,\nwith timing", "Guided,\nwith timing")) +
             scale_y_continuous(breaks=seq(0, 6, by=1)) +
             labs(subtitle="RMSE scores by phrase", x="Phrase", y="RMSE") +
             theme_bw(base_size=27) +
             theme(legend.text=element_text(size=18),
                axis.title=element_text(size=20))

my_plot<-grid.arrange(corr_by_phrase, rmse_by_phrase,ncol=1)
plot_filename<-"scores_by_phrase2.png"
#ggsave(plot_filename, plot = my_plot, device='png', path="data/plots/", width = 12, height = 8)

```

# By subject

```{r}

corr_learners <- ggplot(data=data_im2%>%filter(native=="-0.5"), aes(x=subject, y=corr_nt)) + 
       geom_boxplot(aes(color=as_factor(vocal)), show.legend = FALSE, lwd=1.25,fatten=2) +
       geom_boxplot(data=data_chiro%>%filter(native=="-0.5"),
                    aes(x=subject, y=corr, color=condition), alpha=0.4, show.legend = FALSE, lwd=1.25,fatten=2) +
       scale_color_discrete(name="",labels=c("Voice,\nno timing", "Guided,\nno timing", 
                                     "Non-guided,\nwith timing", "Guided,\nwith timing")) +
             scale_y_continuous(breaks=seq(-0.8, 1, by=0.2)) +
             labs(subtitle="By subject: Non-native", x="Subject", y="") +
             theme_bw(base_size=27) +
             theme(legend.text=element_text(size=18),
                   axis.title=element_text(size=20))


corr_native <- ggplot(data=data_im2%>%filter(native=="0.5"), aes(x=subject, y=corr_nt)) + 
       geom_boxplot(aes(color=as_factor(vocal)), show.legend = FALSE, lwd=1.25,fatten=2) +
       geom_boxplot(data=data_chiro%>%filter(native=="0.5"),
                    aes(x=subject, y=corr, color=condition), alpha=0.4, show.legend = FALSE, lwd=1.25,fatten=2) +

       #scale_color_discrete(name="",labels=c("Voice,\nno timing", "Guided,\nno timing", 
        #                             "Non-guided,\nwith timing", "Guided,\nwith timing")) +
             scale_y_continuous(breaks=seq(-0.8, 1, by=0.2)) +
             labs(subtitle="Native", x="Subject", y="") +
             theme_bw(base_size=27) +
             theme(legend.text=element_text(size=18),
                   axis.title=element_text(size=20))

rmse_learners <- 
      ggplot(data=data_im2%>%filter(native=="-0.5"), aes(x=subject, y=rmse_nt)) + 
       geom_boxplot(aes(color=as_factor(vocal)), show.legend = FALSE, lwd=1.25,fatten=2) +
       geom_boxplot(data=data_chiro%>%filter(native=="-0.5"),
                    aes(x=subject, y=rmse, color=condition), alpha=0.4, show.legend = FALSE, lwd=1.25,fatten=2) +
       #scale_color_discrete(name="",labels=c("Voice,\nno timing", "Guided,\nno timing", 
        #                             "Non-guided,\nwith timing", "Guided,\nwith timing")) +
             scale_y_continuous(breaks=seq(0, 8, by=1)) +
             labs(subtitle="By subject: Non-native", x="Subject", y="") +
             theme_bw(base_size=27) +
             theme(legend.text=element_text(size=18),
                   axis.title=element_text(size=20))

rmse_native <- ggplot(data=data_im2%>%filter(native=="0.5"), aes(x=subject, y=rmse_nt)) + 
       geom_boxplot(aes(color=as_factor(vocal)), show.legend = FALSE, lwd=1.25,fatten=2) +
       geom_boxplot(data=data_chiro%>%filter(native=="0.5"),
                    aes(x=subject, y=rmse, color=condition), alpha=0.4, show.legend = FALSE, lwd=1.25,fatten=2) +

       #scale_color_discrete(name="",labels=c("Voice,\nno timing", "Guided,\nno timing", 
        #                             "Non-guided,\nwith timing", "Guided,\nwith timing")) +
             scale_y_continuous(breaks=seq(0, 8, by=1)) +
             labs(subtitle="Native", x="Subject", y="") +
             theme_bw(base_size=27) +
             theme(legend.text=element_text(size=18),
                   axis.title=element_text(size=20))

my_plot2<-grid.arrange(corr_learners, corr_native, rmse_learners, rmse_native, ncol=2)
plot_filename2<-"scores_by_subject2.png"
#ggsave(plot_filename2, plot = my_plot2, device='png', path="data/plots/", width = 12, height = 8)

```


# For models
```{r}

```


