---
title: "Linear Models"
output: html_notebook
---

# Prerequisites

Run the first part in 04-plots.Rmd to load the data. Load required libraries.

```{r}
library("tidyverse")
library("brms")
```


## Voice imitation vs Guided Chironomic Imitation, no timing

Following the analysis of Chironomic Stylization of Intonation, D'Alessandro et al. 2011, where timing was not considered.

### Correlation
```{r}
priors_corr <- c(set_prior("normal(0, 10)", class="Intercept"),
            set_prior("normal(0, 10)", class="b"),
	          set_prior("cauchy(0, 10)", class="sd"),
	          set_prior("cauchy(0, 10)", class="sigma"),
	          set_prior("lkj(2)", class="cor"))

priors_corr2 <- c(set_prior("normal(0, 10)", class="Intercept"),
            set_prior("normal(0, 10)", class="b"),
	          set_prior("cauchy(0, 10)", class="sd"),
	          set_prior("cauchy(0, 10)", class="sigma"))

# Random intercepts and random slopes, 
# interaction term between condition (vocal 0.5 vs gestural -0.5) and native
cnt_im1 <- brm(formula = corr_nt_z ~ vocal*native + (1+ vocal|subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_corr,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))

### WINNING MODEL
# Random intercepts and random slopes, no interaction between condition and native
cnt_im2 <- brm(formula = corr_nt_z ~ vocal + native + (1+ vocal|subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_corr,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))


# Intercept 1.80, 0.11 error, 1.58 2.03

# Random intercepts only, no interaction between condition and native
cnt_im3 <- brm(formula = corr_nt_z ~ vocal + native + (1 + subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_corr2,
            iter=10000, warmup=2000,
            chains=2, control=list(adapt_delta=0.99, max_treedepth = 15), 
            save_pars=save_pars(all=TRUE))


bayes_factor(cnt_im1, cnt_im2) #.05954 (values below 0.1 favor simpler model)
bayes_factor(cnt_im2, cnt_im3) # 959383630104957

# Null model Native vs Non-native
cnt_im4 <- brm(formula = corr_nt_z ~ native + (1+ vocal|subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_corr,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))

bayes_factor(cnt_im4, cnt_im2) # 32.57227


# Null model, condition only
cnt_im5 <- brm(formula = corr_nt_z ~ vocal + (1+ vocal|subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_corr,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))

bayes_factor(cnt_im5, cnt_im2) # 75.566

# Comparin with LOO
loo_cnt_im <- loo(cnt_im1, cnt_im2, cnt_im4, cnt_im5)
loo_cnt_im
```

### RMSE, no timing

```{r}
priors_rmse <- c(set_prior("normal(0, 10)", class="Intercept"),
            set_prior("normal(0, 10)", class="b"),
	          set_prior("cauchy(0, 10)", class="sd"),
	          set_prior("cauchy(0, 10)", class="sigma"),
	          set_prior("lkj(2)", class="cor"))

priors_rmse2 <- c(set_prior("normal(0, 10)", class="Intercept"),
            set_prior("normal(0, 10)", class="b"),
	          set_prior("cauchy(0, 10)", class="sd"),
	          set_prior("cauchy(0, 10)", class="sigma"))

priors_rmse3 <- c(set_prior("normal(0, 10)", class="Intercept"),
	          set_prior("cauchy(0, 10)", class="sd"),
	          set_prior("cauchy(0, 10)", class="sigma"),
	          set_prior("lkj(2)", class="cor"))

# Random intercepts and random slopes, 
# interaction term between condition (vocal 0.5 vs gestural -0.5) and native
rnt_im1 <- brm(formula = log_rnt ~ vocal*native + (1+ vocal|subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_rmse,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))

# Random intercepts and random slopes, no interaction between condition and native
rnt_im2 <- brm(formula = log_rnt ~ vocal+native + (1+ vocal|subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_rmse,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))
bayes_factor(rnt_im1, rnt_im2) # 0.03845

# Random intercepts only, no interaction between condition and native
rnt_im3 <- brm(formula = log_rnt ~ vocal+native + (1+subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_rmse2,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))
bayes_factor(rnt_im2, rnt_im3) #1126115362816631.50000

# Null model Native vs Non-native
rnt_im4 <- brm(formula = log_rnt ~ native + (1+ vocal|subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_rmse,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))
bayes_factor(rnt_im4, rnt_im2) #5.4517

# Null model, condition only
rnt_im5 <- brm(formula = log_rnt ~ vocal + (1+ vocal|subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_rmse,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))
bayes_factor(rnt_im5, rnt_im2) #96.445

rnt_im6 <- brm(formula = log_rnt ~ 1 + (1+ vocal|subject) + (1|pid), 
            data=data_im, family=gaussian(), prior=priors_rmse3,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))
bayes_factor(rnt_im5, rnt_im6) #.18


# Comparin with LOO
loo_rnt_im <- loo(rnt_im1, rnt_im2, rnt_im4, rnt_im5, rnt_im6)
```

## Chironomic Imitation - Guided & Non-Guided

Comparing blind and guided gestures and seeing the effect of timing on the difficulty of the task.

### Correlation, with timing considered
```{r}
priors_corr <- c(set_prior("normal(0, 10)", class="Intercept"),
            set_prior("normal(0, 10)", class="b"),
	          set_prior("cauchy(0, 10)", class="sd"),
	          set_prior("cauchy(0, 10)", class="sigma"),
	          set_prior("lkj(2)", class="cor"))

priors_corr2 <- c(set_prior("normal(0, 10)", class="Intercept"),
            set_prior("normal(0, 10)", class="b"),
	          set_prior("cauchy(0, 10)", class="sd"),
	          set_prior("cauchy(0, 10)", class="sigma"))

# Random intercepts and random slopes, 
# interaction term between condition (vocal 0.5 vs gestural -0.5) and native
corr_ch1 <- brm(formula = corr_z ~ guide*native + (1+ guide|subject) + (1|pid), 
            data=data_chiro, family=gaussian(), prior=priors_corr,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))

# Random intercepts and random slopes, no interaction between condition and native
corr_ch2 <- brm(formula = corr_z ~ guide+ native + (1+ guide|subject) + (1|pid), 
            data=data_chiro, family=gaussian(), prior=priors_corr,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))

# Random intercepts only, no interaction between condition and native
corr_ch3 <- brm(formula = corr_z ~ guide + native + (1 + subject) + (1|pid), 
            data=data_chiro, family=gaussian(), prior=priors_corr2,
            iter=10000, warmup=2000,
            chains=2, control=list(adapt_delta=0.99, max_treedepth = 15), 
            save_pars=save_pars(all=TRUE))

bf12<-bayes_factor(corr_ch1, corr_ch2) # .295
bf23<-bayes_factor(corr_ch2, corr_ch3) # 36.1496 - strong evidence that more complex model is better

# Null model Native vs Non-native
corr_ch4 <- brm(formula = corr_z ~ native + (1+ guide|subject) + (1|pid), 
            data=data_chiro, family=gaussian(), prior=priors_corr,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))
bf42<-bayes_factor(corr_ch4, corr_ch2) #1.61497

# Null model, condition only
corr_ch5 <- brm(formula = corr_z ~ guide + (1+ guide|subject) + (1|pid), 
            data=data_chiro, family=gaussian(), prior=priors_corr,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))
bf52<-bayes_factor(corr_ch5, corr_ch2) #13.2018

loo_corr_ch<-loo(corr_ch1, corr_ch2, corr_ch4, corr_ch5)

```

### RMSE, with timing considered - guided vs non-gudied
```{r}
priors_rmse <- c(set_prior("normal(0, 10)", class="Intercept"),
            set_prior("normal(0, 10)", class="b"),
	          set_prior("cauchy(0, 10)", class="sd"),
	          set_prior("cauchy(0, 10)", class="sigma"),
	          set_prior("lkj(2)", class="cor"))

priors_rmse2 <- c(set_prior("normal(0, 10)", class="Intercept"),
            set_prior("normal(0, 10)", class="b"),
	          set_prior("cauchy(0, 10)", class="sd"),
	          set_prior("cauchy(0, 10)", class="sigma"))

priors_rmse3 <- c(set_prior("normal(0, 10)", class="Intercept"),
	          set_prior("cauchy(0, 10)", class="sd"),
	          set_prior("cauchy(0, 10)", class="sigma"),
	          set_prior("lkj(2)", class="cor"))

# Random intercepts and random slopes, 
# interaction term between condition (vocal 0.5 vs gestural -0.5) and native
r_ch1 <- brm(formula = log_r ~ guide*native + (1+ guide|subject) + (1|pid), 
            data=data_chiro, family=gaussian(), prior=priors_rmse,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))

# Random intercepts and random slopes, no interaction between condition and native
r_ch2 <- brm(formula = log_r ~ guide+ native + (1+ guide|subject) + (1|pid), 
            data=data_chiro, family=gaussian(), prior=priors_rmse,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))

# Random intercepts only, no interaction between condition and native
r_ch3 <- brm(formula = log_r ~ guide + native + (1 + subject) + (1|pid), 
            data=data_chiro, family=gaussian(), prior=priors_rmse2,
            iter=10000, warmup=2000,
            chains=2, control=list(adapt_delta=0.99, max_treedepth = 15), 
            save_pars=save_pars(all=TRUE))

bfr12<-bayes_factor(r_ch1, r_ch2)
bfr23<-bayes_factor(r_ch2, r_ch3)

# Null model Native vs Non-native
r_ch4 <- brm(formula = log_r ~ native + (1+ guide|subject) + (1|pid), 
            data=data_chiro, family=gaussian(), prior=priors_rmse,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))
bfr42<-bayes_factor(r_ch4, r_ch2)

# Null model, condition only
r_ch5 <- brm(formula = log_r ~ guide + (1+ guide|subject) + (1|pid), 
            data=data_chiro, family=gaussian(), prior=priors_rmse,
            iter=10000, warmup=2000, 
            chains=2, control=list(adapt_delta=0.99), save_pars=save_pars(all=TRUE))
bfr52<-bayes_factor(r_ch5, r_ch2) 

loo_r_ch<-loo(r_ch1, r_ch2, r_ch4, r_ch5)

```
